---
title: "Discarded"
author: "Batoule Hyjazie"
date: "05/04/2021"
output: html_document
---

### 2.2.1.2 Linear Mixed Model

```{r 2.2.1 Frequentist Approach}

library(lmerTest)

osmiafreq <- lmer(surv.ratio ~ s.type + (1|s.ID), data=Osmia)
summary(osmiafreq)
```

Firstly, based on the scaled residuals of the first model that was run, it is obvious that the distribution is not Gaussian. Because of this, we will need to run a generalized linear mixed model.

#### 2.2.1.2.1 Plot of the Data

```{r 2.2.1.2.1 Plot of the Data}

library(ggplot2)
library(lattice)
library(tidyverse)
library(patchwork)
```

#### 2.2.1.2.2 Testing Distributions

```{r 2.2.1.2.1 Testing Distributions}

ggplot(Osmia, aes(x = s.type, y = log(1 + surv.ratio))) +
  geom_boxplot() +
  theme_bw()

Osmia_means <- with(Osmia, tapply(surv.ratio, list(s.type), mean))
summary(Osmia_means)
```

```{r}
library(effects)
plot(allEffects(osfreqglmm))
```

```{r 2.2.1.1 Distribution}
qqp(Osmia$No.surv.osmia/Osmia$No.cells, "norm")
fitBinom <- fitdist(Osmia$surv.ratio, dist="binom", fix.arg=list(size=219), start=list(prob=0.5))
qqp(Osmia$surv.ratio, "binom", size=219, prob=0.5, fitBinom$estimate)
```

```{r 2.2.1.1 GLMM Simple, include = FALSE}
osmiaglmm <- glmer(No.surv.osmia/No.cells ~ s.type + (1|s.ID), weights = No.cells, family = binomial(link="logit"), data=Osmia)
summary(osmiaglmm)
overdisp.glmer(osmiaglmm)
```

```{r 3.2.1.1 Key Assumptions Box Plot Residual Plot, fig.cap="\\label{fig:figs}Residuals versus Fitted Values of Final Osmia Survival Model"}
boxplot(resid.weed_pois~trmt,data=rcbd, main="Homogeneity of Residual Variance by Treatment Group", xlab="Treatment Groups", ylab="Residuals")
```

### 2.1.1 Total Nesting Structures

**The "Total Nesting Structures.xlsx" data set contains all of the information regarding the species that occupied the nest blocks but does not include any information on the survival of these species. This data set is useful because it provides information on the number of nests that were installed in each site and each site type. A variety of hymenopterans nested within the nesting structures including wasps (genus unknown), bees such as *Megachile* spp. and of course numerous *Osmia* spp. For the purposes of this analysis, we will focus on *Osmia* spp. offspring survival.**

```{r 3.2.1 Analysis of Deviance Table (Type III Wald Chisquare Test)}

# Output from summary glmm is anti-conservative so we use a wald test p-values which are not as strongly biased as the z-test from the summary
library(car)
 #No intercept, testing if fixed effect reduces amount of residual variation (fitting a model with no parameter and comparing with the parameter of interest) You compare the deviance between the two and get an estimate of the p-values. The intercept is an estimate it doesn't explain any variance (knowing if the intercept differs from 0 is not important info0, will tell you if the different levels within a factor different from one another)
```

```{r 3.2.1 Frequentist Results Tables}

plot_model(osmiaglmm, type = "eff", show.intercept = TRUE, show.legend = TRUE, colors = "lightblue")
plot_model(osmiaglmm, type = "diag", show.intercept = TRUE, show.data = TRUE, show.legend = TRUE, colors = "Set2")
```

```{r Frequentist Results GLMM Figure, fig.cap="\\label{fig:figs}*Osmia* spp. survival versus habitat type using GLMM Estimates"}

plot_model(osmiaglmm, show.p = TRUE, vline = "lightblue", show.intercept = TRUE, colors = "blue", title = "", axis.labels = c("Orchard Sites", "Intercept"))
```

